Estimating Comparative Advantage in Improved Seed Adoption: Hybrid Maize in Ethiopia

### 2021-11-24 paper.tex

Figure \ref{map:regions} shows the spatial distribution of the locations of the our households of study. As previously mentioned these are households that grow either improved or conventional maize and that are observed for all three rounds of the survey. Most households come from the northwest region of the

@@

Table \ref{tbl:summary} shows a set of the summary statistics for the sample of house

>>>>

Figure \ref{map:regions} shows the spatial distribution of the locations of the our households of study. As previously mentioned these are households that grow either improved or conventional maize and that are observed for all three rounds of the survey. Most households come from the northwest region of Amhara, Tigray and Oromiya which is consistent with where maize is mostly grown in Ethiopia \citep{Abate2015-rj}.

@@

Table \ref{tbl:summary} shows a set of summary statistics for our sample.

% Explain summary stats
% different definitions of yields
% hybrid and trajectories
